\documentclass[10pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern} % Modern Roman font
\usepackage[margin=1in]{geometry}
\usepackage{hyperref} % For clickable links
\usepackage{enumitem} % For custom list environments
\usepackage{xcolor} % For colors

% Define a custom color for headings
\definecolor{darkblue}{rgb}{0.0, 0.0, 0.55}

\title{\textcolor{darkblue}{\textbf{Backend Interview Challenge}}}
\author{Stanley Shikwambi} % No author
\date{18 July 2025} % No date

\begin{document}

\maketitle
\thispagestyle{empty} % No page number on the first page

\begin{center}
    \textit{You are what you do, not what you say you'll do - Carl Jung}
\end{center}

\vspace{1cm}

Your task is to demonstrate your frontend development skills by interacting with a provided backend service. The service provides an API that pulls data from a database that stores details about different football players.

\section*{\textcolor{darkblue}{Provided Backend Service Details}}
The existing backend service is already running and accessible at:
\textbf{\texttt{http://0.0.0.0:8000}}

\subsection*{Authentication:}
This service requires authentication. To get an API key, make a \texttt{POST} request to \texttt{/auth}. You will receive a unique API key \texttt{api\_key} that must be passed in the \texttt{x-api-key} header for all subsequent requests to protected endpoints.

\subsection*{Available Routes:}
\begin{itemize}[label=\textbullet, leftmargin=*, itemsep=0.5em]
    \item \texttt{POST /auth}: Get an API key.
    \item \texttt{POST /createPlayer}: Create a new player.
    \item \texttt{GET /getPlayers}: Get a list of all players.
    \item \texttt{GET /getPlayer/\{id\}}: Get a single player by ID.
    \item \texttt{PUT /updatePlayer/\{id\}}: Update an existing player.
    \item \texttt{DELETE /deletePlayer/\{id\}}: Delete a player.
\end{itemize}

\section*{\textcolor{darkblue}{Your Challenge}}
\begin{enumerate}[label=\arabic*., leftmargin=*, itemsep=0.5em]
    \item \textbf{Authentication and Caching:} Implement a mechanism to obtain an API key from the \texttt{/auth} endpoint. This API key has a Time-To-Live (TTL) of 60 minutes. You will need to implement a caching strategy to store and reuse this token, and also a refresh strategy to obtain a new token when the current one expires.
    \item \textbf{Data Retrieval and Augmentation:} Call the \texttt{GET /getPlayers} route from the provided backend service. For each player retrieved, add two new fields with any data you deem relevant (e.g., calculated age, a new statistic, a derived property).
    \item \textbf{New Backend Service:} Build a new backend service (using any stack of your choice) that exposes a single \texttt{GET /new-players} route. This route should return the list of players with the two new fields you added.
\end{enumerate}

\section*{\textcolor{darkblue}{Guidelines}}
\begin{itemize}[label=\textbullet, leftmargin=*, itemsep=0.5em]
    \item You may use any backend stack or framework of your choice (e.g., Node.js, Python, Go, Java).
    \item You are allowed to use AI tools to assist you, but please do not use them to generate the entire solution. We are interested in seeing your problem-solving approach and coding style.
    \item Focus on clean code, good practices, and efficient data handling.
\end{itemize}

\vspace{1cm}
\begin{center}
    \textit{Good luck and have fun!}
\end{center}

\end{document}
