\documentclass[10pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern} % Modern Roman font
\usepackage[margin=1in]{geometry}
\usepackage{hyperref} % For clickable links
\usepackage{enumitem} % For custom list environments
\usepackage{xcolor} % For colors

% Define a custom color for headings
\definecolor{darkblue}{rgb}{0.0, 0.0, 0.55}

\title{\textcolor{darkblue}{\textbf{Frontend Interview Challenge}}}
\author{Stanley Shikwambi} % No author
\date{18 July 2025} % No date

\begin{document}

\maketitle
\thispagestyle{empty} % No page number on the first page

\begin{center}
    \textit{You are what you do, not what you say you'll do - Carl Jung}
\end{center}

\vspace{1cm}

Your task is to demonstrate your frontend development skills by interacting with a provided backend service. The service provides an API that pulls data from a database that stores details about different football players.

\section*{\textcolor{darkblue}{Backend Service Details}}
The backend service is already running and accessible at:
\textbf{\texttt{http://0.0.0.0:8000}}

\subsection*{Authentication:}
This service requires authentication. To get an API key, make a \texttt{POST} request to \texttt{/auth}. You will receive a unique API key \texttt{api\_key} that must be passed in the \texttt{x-api-key} header for all subsequent requests to protected endpoints.

\subsection*{Available Routes:}
\begin{itemize}[label=\textbullet, leftmargin=*, itemsep=0.5em]
    \item \texttt{POST /auth}: Get an API key.
    \item \texttt{POST /createPlayer}: Create a new player.
    \item \texttt{GET /getPlayers}: Get a list of all players.
    \item \texttt{GET /getPlayer/\{id\}}: Get a single player by ID.
    \item \texttt{PUT /updatePlayer/\{id\}}: Update an existing player.
    \item \texttt{DELETE /deletePlayer/\{id\}}: Delete a player.
\end{itemize}

\section*{\textcolor{darkblue}{Your Challenge}}
\begin{enumerate}[label=\arabic*., leftmargin=*, itemsep=0.5em]
    \item Your primary task is to consume data from the backend. Specifically, make a request to the \textbf{\texttt{GET /getPlayers}} route.
    \item Take the information received from this route and display it in any fashion you deem appropriate. Feel free to be creative with the presentation and user interface.
\end{enumerate}

\section*{\textcolor{darkblue}{Guidelines}}
\begin{itemize}[label=\textbullet, leftmargin=*, itemsep=0.5em]
    \item You may use any frontend stack or framework of your choice (e.g., React, Vue, Angular, vanilla JavaScript).
    \item You are allowed to use AI tools to assist you, but please do not use them to generate the entire solution. We are interested in seeing your problem-solving approach and coding style.
    \item Focus on clean code, good practices, and a functional user interface.
\end{itemize}

\vspace{1cm}
\begin{center}
    \textit{Good luck and have fun!}
\end{center}

\end{document}
